Fig2

### 2020-02-20 analysis/figure-2.Rmd
suppl table 1

suppletable1 <- allDEG %>%
  filter(gene %in% HYPcandidategenes) %>%
  group_by(sex, tissue, comparison) %>%
  summarize(genes = str_c(gene, collapse = " ")) %>%
  pivot_wider(names_from = comparison, values_from = genes ) %>%
  select(sex, tissue, control_bldg, lay_inc.d3, inc.d3_inc.d9,
         inc.d9_inc.d17, hatch_n5)  %>%
  arrange(sex, tissue)
suppletable1

>>>>

suppletable1 <- allDEG %>%
  filter(gene %in% HYPcandidategenes, 
         tissue == "hypothalamus") %>%
  group_by(sex, tissue, comparison) %>%
  summarize(genes = str_c(gene, collapse = " ")) %>%
  pivot_wider(names_from = comparison, values_from = genes ) %>%
  select(sex, tissue, control_bldg,  
         inc.d9_inc.d17, hatch_n5)  %>%
  arrange(sex, tissue)
suppletable1
